---
title: "Cluster_Identification"
output: html_document
date: '2023-07-02'
---

Reference
Website: https://bioinformagician.org/
Github: https://github.com/kpatel427

Vignettes
https://satijalab.org/seurat/articles/pbmc3k_tutorial.html#finding-differentially-expressed-features-cluster-biomarkers-
https://hbctraining.github.io/In-depth-NGS-Data-Analysis-Course/sessionIV/lessons/SC_marker_identification.html

```{r}
library(Seurat)
library(SeuratDisk)
```

Load data
```{r}
ifnb_harmony = readRDS(filename)
```

Visualize data
```{r}
View(ifnb_harmony@meta.data)
clusters = DimPlot(ifnb_harmony, reduction = 'umap', group.by = 'seurat_clusters', label = T)
condition = DimPlot(ifnb_harmony, reduction = 'umap', group.by = 'condition')
condition|clusters
```

findAll markers: Compare one cluster vs all others 
```{r}
FindAllMarkers(ifnb_harmony,
               logfc.threshold = 0.25, #min logfc 
               min.pct = 0.1, #genes that are detected on 50% frequency across clusters
               only.pos = T,
               test.use = 'DESeq2',
               slot = 'counts')
```

findConserved markers: Compare one cluster vs all others when you have two conditions (ex. separates cells by condition and does the analysis with the splitted data)
```{r}
markers_cluster3 = FindConservedMarkers(ifnb_harmony,
                                        ident.1 =  3, #cluster
                                        grouping.var = 'stim') #condition
head(markers_cluster3)

#Visualize top features
FeaturePlot(ifnb_harmony, features = c('FCGR3A'), min.cutoff = 'q10')
```

Rename cluster 3 Ident (names)
```{r}
Idents(ifnb_harmony)
RenameIdents(ifnb_harmony, '3' = 'CD16 Mono')
DimPlot(ifnb_harmony, reduction = 'umap', label = T)
```

Some cells already have annotations provided in the metadata (check for them before calculating again)
```{r}
Idents(ifnb_harmony) = ifnb_harmony@meta.data$seurat_annotations
Idents(ifnb_harmony)
DimPlot(ifnb_harmony, reduction = 'umap', label = T)
```

Find markers between conditions (findMarkers function to compare one cluster vs another)
```{r}
ifnb_harmony$celltype.cnd = paste0(ifnb_harmony$seurat_annotations, '_', ifnb_harmony$stim)
View(ifnb_harmony@meta.data)
Idents(ifnb_harmony) = ifnb_harmony$celltype.cnd
DimPlot(ifnb_harmony, reduction = 'umap', label = T)

b.interferon.response = FindMarkers(ifnb_harmony, ident.1 = "CD16 Mono_STIM", ident.2 = "CD16 Mono_CTRL")
head(b.interferon.response)
```

Plotting conserved features vs DE features between conditions
```{r}
FeaturePlot(ifnb_harmony, features = c('FCGR3A', 'AIF1', 'IFIT1'), split.by = 'stim', min.cutoff = 'q10')
```

