---
title: "scRNAseq integration"
output: html_document
date: '2023-07-02'
---

Data: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE180665

References
https://satijalab.org/seurat/articles/integration_introduction.html
https://github.com/kpatel427/YouTubeTutorials/blob/main/singleCell_integration.R

```{r}
library(Seurat)
library(ggplot2)
library(tidyverse)
library(gridExtra)
```

Get data location where are all files
```{r}
dirs = list.dirs(path = 'data/', recursive = F, full.names = F)
```

Loop to integrate several matrices and create several Seurat objects
```{r}
for (x in dirs) {
  name = gsub('_filtered_feature_bc_matrix', '', x)
  cts = ReadMtx(mtx = paste0('data/', x, '/matrix.mtx.gz'),
          features = paste0('data/', x, '/features.tsv.gz'),
          cells = paste0('data/', x, '/barcodes.tsv.gz'))
  
  #Create Seurat object
  assign(name, CreateSeuratObject(counts = cts))
}
```

Merge seurat objects (not integrate) just to do QC and others changes in all seurat object simultaneosly
```{r}
merge_seurat = merge(HB17_background, y = c(HB17_PDX, HB17_tumor, HB30_PDX, HB30_tumor, HB53_background,
                                            HB53_tumor),
                     add.cell.ids = ls()[3:9],
                     project = 'HB')

merge_seurat
```

Create Sample column to identify experiments and barcodes
```{r}
merge_seurat$sample = rownames(merge_seurat@meta.data)
merge_seurat@meta.data = separate(merge_seurat@meta.data, col = "sample", into = c("Patient", "Type","Barcode"), sep = "_")
View(merge_seurat@meta.data)
```

QC & filtering (mitochondrial genes are good but also look for other sources to check for quality control)
```{r}
merged_seurat$mitoPercent = PercentageFeatureSet(merge_seurat, pattern = '^MT-')
merge_seurat_filtered = subset(merge_seurat, subset = nCount_RNA > 800 & nFeatures_RNA > 500 & mitoPercent < 10)
merge_seurat_filtered
```

Preprocessing steps (for more info on this check workflows files)
```{r}
merge_seurat_filtered = NormalizeData(object = merge_seurat_filtered)
merge_seurat_filtered = FindVariableFeatures(object = merge_seurat_filtered)
merge_seurat_filtered = ScaleData(object = merge_seurat_filtered)
merge_seurat_filtered = RunPCA(object = merge_seurat_filtered)
ElbowPlot(merge_seurat_filtered)
merge_seurat_filtered = FindNeighbors(object = merge_seurat_filtered, dims = 1:20)
merge_seurat_filtered = FindClusters(object = merge_seurat_filtered)
merge_seurat_filtered = RunUMAP(object = merge_seurat_filtered, dims = 1:20)
```

Batch effect (check if clusters are due to technical differences (ex. patient) instead of biological variation)
```{r}
DimPlot(merge_seurat_filtered, reduction = "umap", group.by = "Patient")
DimPlot(merge_seurat_filtered, reduction = "umap", group.by = "Type",
        cols = c('red', 'green', 'blue'))
grid.arrange(p1, p2, ncol=2, nrow=2)
```

Remove batch effect
```{r}
obj.list = SplitObject(merge_seurat_filtered, split.by = "Patient")
for (i in 1:length(obj.list)) {
  obj.list[[i]] = NormalizeData(object = obj.list[[i]])
  obj.list[[i]] = FindVariableFeatures(object = obj.list[[i]])
}

#Select integration features
features = SelectIntegrationFeatures(object.list = object.list)
anchors = FindIntegrationAnchors(object.list = obj.list, #CCA method
                       anchor.features = features)
seurat_integrated = IntegrateData(anchorset = anchors)

seurat.integrated = ScaleData(seurat_integrated)
seurat_integrated = RunPCA(object = seurat_integrated)
seurat_integrated = RunUMAP(object = seurat_integrated, dims = 1:50) #Arbitrary using 50 dimensions
```

Visualize batch effect removal
```{r}
p3 = DimPlot(seurat_integrated, reduction = 'umap', group.by = 'Patient')
p4 = DimPlot(seurat_integrated, reduction = 'umap', group.by = 'Type')

grid.arrange(p1, p2, p3, p4, ncol=2, nrow=2)

```

